Modular analysis of gene expression data with GNU R or Matlab

### 2009-10-06 isanote/modular.tex
ISA note updated, a figure was added.

@@

\title[Modular analysis]{Modular analysis of gene expression data with
  GNU R or Matlab}
\author[G\'abor Cs\'ardi \textit{et~al}]{G\'abor Cs\'ardi\,,$^{1,2}$,
  Zolt\'an Kutalik\,$^{1,2}$ and Sven Bergmann\,$^{1,2}$}
\address{$^{1}$Department of Medical Genetics, and 
  $^{2}$Swiss Institute of Bioinformatics,
  University of Lausanne, Rue de Bugnon 27 - DGM 328, CH-1005 Lausanne,
  Switzerland.}

@@

What is biclustering.
What is the ISA.

@@

Normalization.

Random and smart seeding.

The ISA iteration.

Merging the modules.

The robustness measure and filtering the modules.

Module trees.

@@

\subsection{Workflow}

@@

@@

Expression plots, GO tree plots, module tree plots, HTML summary
generation.

>>>>

\newcommand{\Rpackage}{`\texttt{#1}'}

@@

\title[Modular analysis]{Modular analysis of gene expression data with
  GNU R or Matlab}
\author[G\'abor Cs\'ardi \textit{et~al}]{G\'abor Cs\'ardi\,,$^{1,2}$,
  Zolt\'an Kutalik\,$^{1,2}$ and Sven Bergmann\,$^{1,2}$}
\address{$^{1}$Department of Medical Genetics, and 
  $^{2}$Swiss Institute of Bioinformatics,
  University of Lausanne, Rue de Bugnon 27, CH-1005 Lausanne,
  Switzerland.}

@@

% What is biclustering.

Biclustering is the idea of clustering the rows and the columns of a
data matrix, together, usually not independently. In other words, the
goal of a biclustering algorithm is to find blocks in the reordered
data matrix that have, such that the blocks have correlated rows and
columns. It is important to note that these blocks (or biclusters)
have context, i.e. the rows only need to be correlated across the
columns of the block, but not across other columns of the data matrix;
and vice-versa.

When it comes to gene expression data, a bicluster means a subset of
genes ($G$) (or probes, probe sets) and a subset of samples ($S$),
such that genes $G$ are exactly coexpressed across $S$ and samples $S$
have correlated expression profile exactly across $G$.

% What is the ISA.

The Iterative Signature Algorithm (ISA)~\cite{sa,isa,ismod} is a 
powerful biclustering algorithm. It is able to identify biclusters
that overlap and it is resilient to noise.

In this short note, we introduce the \Rpackage{isa2} and
\Rpackage{eisa} GNU R~\cite{R} packages; these implement the ISA
biclustering method, provide a convenient interface to run it using
the BioConductor~\cite{BioC} software package, and also contain
visualization tools.

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{isa2workflow3}
\caption{}
\label{fig:workflow}
\end{figure*}

% Batch correction

% Normalization.

% Random and smart seeding.

% The ISA iteration.

% Merging the modules.

% The robustness measure and filtering the modules.

% Module trees.

@@

\subsection{Work flow}

@@

\subsubsection{The simple work flow}

\subsubsection{The detailed work flow}

@@

Expression plots, GO tree plots, module tree plots, HTML summary
generation. ExpressionView.
